A formal treatment of bidirectional typing\texorpdfstring{\thanks{The work is supported by the National Science and Technology Council of Taiwan under grant NSTC 112-2221-E-001-003-MY3.}}{}

### 2023-12-25 tex/ESOP24/S8-future.tex
[ tex ] sort => type
[ tex ] Add Acknowledgement

\paragraph{Polymorphic types}
In the case of languages like \SystemF and others that permit type-level variable binding, we can start with the notion of polymorphic signature, as introduced by \citet{Hamana2011}---\begin{inlineenum}
  \item each type construct in a signature is specified by a binding arity with a single sort $*$, and
  \item a term construct can employ a pair of extension contexts for term variables and type variables.
\end{inlineenum}

@@

%Such aspects  may continue to require creativity from the designer of type systems whereas its implementation could be automated entirely.

%\subsection*{Acknowledgement}
%We thank Nathanael Arkor for the useful conversation.
%James Wood
%We thank Kuen-Bang {Hou (Favonia)} for his comments and suggestions.

>>>>

\paragraph{Polymorphic types}
In the case of languages like \SystemF and others that permit type-level variable binding, we can start with the notion of polymorphic signature, as introduced by \citet{Hamana2011}---\begin{inlineenum}
  \item each type construct in a signature is specified by a binding arity with only one type $*$, and
  \item a term construct can employ a pair of extension contexts for term variables and type variables.
\end{inlineenum}

@@

\begin{credits}
\subsubsection{Acknowledgements.}
We thank Kuen-Bang {Hou (Favonia)} and anonymous reviewers for their comments and suggestions.
\end{credits}
